---
title: "Election Poll Data Analysis Report"
author: "Tarik"
output: html_document
---

## Load the data and define variables

```{r, message=FALSE, warning=FALSE}
library(dslabs)
data("polls_us_election_2016")

my_first <- "Tar??k"
my_birth_year <- 2003

k <- (nchar(my_first) + my_birth_year) %% 15 + 8
```

## Value of k

```{r}
k
```

## Original data set: display k rows

```{r}
if (k %% 2 == 0) {
  head(polls_us_election_2016, k)
} else {
  tail(polls_us_election_2016, k)
}
```

## NA analysis for the original data set

### Total number of NA values in the entire data set

```{r}
sum(is.na(polls_us_election_2016))
```

### Number of NA values per column (top 8, sorted from largest to smallest)

```{r}
na_per_col <- colSums(is.na(polls_us_election_2016))
head(sort(na_per_col, decreasing = TRUE), 8)
```

## Create a new data frame by replacing NA values

```{r}
new_data <- polls_us_election_2016

for (i in 1:ncol(new_data)) {
  if (is.numeric(new_data[[i]])) {
    new_data[[i]][is.na(new_data[[i]])] <- my_birth_year + k
  } else if (is.character(new_data[[i]]) || is.factor(new_data[[i]])) {
    new_data[[i]] <- as.character(new_data[[i]])
    new_data[[i]][is.na(new_data[[i]])] <- paste0(my_first, "_", k)
  }
}
```

## New data frame outputs

### 1. Display k rows of the new data frame

```{r}
if (k %% 2 == 0) {
  head(new_data, k)
} else {
  tail(new_data, k)
}
```

### 2. Total number of NA values remaining in the new data frame

```{r}
sum(is.na(new_data))
```

### 3. Result of anyNA(new_data)

```{r}
anyNA(new_data)
```

Note: I used AI tools to assist in formatting the R Markdown document and clarifying assignment instructions. I used R code to analyze and verify the analysis process and the final outputs.
