---
title: "Assignment 1"
---

This assignment consists of two main parts: a video summary with related questions and a set of R programming tasks performed on a specific dataset.

## A. **Video Summary**

Video Title: [Veri Bilimi ve Endüstri Mühendisliği Üzerine Sohbetler - Mustafa Baydoğan & Erdi Daşdemir](https://www.youtube.com/watch?v=1Mvkn71dhaA)

### **Overview**

The video discusses the relationship between Industrial Engineering and Data Science and explains how these two fields work together to solve real-world problems. The speaker emphasizes that data should not be analyzed alone. Instead, engineers should understand the system, process, or business environment behind the data. Industrial Engineers are well prepared for this because their education includes mathematics, statistics, optimization, and problem-solving methods. These skills help them analyze complex systems and make decisions based on data.

Another important point in the video is that prediction is only one part of the process. In many business situations, the main goal is not only to forecast what will happen but also to decide what action should be taken. For this reason, the lecture highlights the importance of Prescriptive Analytics, which combines prediction with optimization and decision making. This approach helps companies choose the best strategy based on available data and possible future scenarios.

The video also presents several practical examples to explain how data science is used in different industries. One example focuses on the manufacturing sector, where engineers predict whether wood will bend during production. By identifying this problem early, companies can take preventive actions and reduce financial losses. Another example comes from the energy sector, where electricity production and consumption must be balanced at all times. Accurate demand forecasts are important because incorrect predictions can lead to significant economic costs.

In addition, the lecture discusses how data science is used in online retail platforms. Companies analyze customer behavior, product popularity, and inventory information to decide how products should be ranked on websites. The goal is to show customers the most relevant products while also maximizing sales and managing stock levels effectively.

Finally, the speaker explains that in many business environments, models should be understandable and explainable. Even if complex machine learning models can achieve high accuracy, companies often prefer simpler models that can be clearly explained to managers or decision makers. The lecture also highlights that learning data science requires practical experience. Working with real, imperfect datasets and solving real problems is essential for developing strong analytical skills.

### **Summary**

-   Industrial Engineers combine data analysis, optimization, and decision making.

-   Data science is applied in manufacturing, energy markets, and online retail.

-   Prescriptive Analytics helps decide the best action based on predictions.

-   In business, interpretable models are often preferred.

-   Practical experience with real data is essential to learn data science.

### **Questions & Answers**

1.  Why is "interpretability" considered a priority in Industrial Engineering data science projects compared to using "black-box" models?

***Answer:*** Interpretability is vital because business decisions often require justification for stakeholders or regulatory compliance. If a model's logic is hidden, it becomes nearly impossible to perform root cause analysis or build trust with decision-makers when errors occur.

2.  According to the video, which type of analytics focuses on "What should we do?" by combining predictions with optimization?

<!-- -->

A)  Descriptive Analytics

B)  Predictive Analytics

C)  Prescriptive Analytics

D)  Diagnostic Analytics

**Answer: C) Prescriptive Analytics**

------------------------------------------------------------------------

## B. **Homework** 

### **Load the data and define variables**

```{r, message=FALSE, warning=FALSE}
library(dslabs)
data("polls_us_election_2016")

my_first <- "Tarık"
my_birth_year <- 2003

k <- (nchar(my_first) + my_birth_year) %% 15 + 8
```

### **Value of k**

```{r}
k
```

### **Original data set: display k rows**

```{r}
if (k %% 2 == 0) {
  head(polls_us_election_2016, k)
} else {
  tail(polls_us_election_2016, k)
}
```

### **NA analysis for the original data set**

#### Total number of NA values in the entire data set

```{r}
sum(is.na(polls_us_election_2016))
```

#### Number of NA values per column (top 8, sorted from largest to smallest)

```{r}
na_per_col <- colSums(is.na(polls_us_election_2016))
head(sort(na_per_col, decreasing = TRUE), 8)
```

### **Create a new data frame by replacing NA values**

```{r}
new_data <- polls_us_election_2016

for (i in 1:ncol(new_data)) {
  if (is.numeric(new_data[[i]])) {
    new_data[[i]][is.na(new_data[[i]])] <- my_birth_year + k
  } else if (is.character(new_data[[i]]) || is.factor(new_data[[i]])) {
    new_data[[i]] <- as.character(new_data[[i]])
    new_data[[i]][is.na(new_data[[i]])] <- paste0(my_first, "_", k)
  }
}
```

### **New data frame outputs**

#### 1. Display k rows of the new data frame

```{r}
if (k %% 2 == 0) {
  head(new_data, k)
} else {
  tail(new_data, k)
}
```

#### 2. Total number of NA values remaining in the new data frame

```{r}
sum(is.na(new_data))
```

#### 3. Result of anyNA(new_data)

```{r}
anyNA(new_data)
```

Note: I used AI tools to assist in formatting the R Markdown document and clarifying assignment instructions. I used R code to analyze and verify the analysis process and the final outputs.

